The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
acks
Sub->secondary
Changes to ack

              \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \hline

@@

\section{Acknowledgements}
We would like to thank company A and that project at GU.

>>>>

              \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Secondary}}        \\ \hline

@@

\section{Acknowledgements}
We would like to thank company A for allowing us to conduct this study in cooperation with them. We would also like to thank associate professor Imed Hammouda for assisting us with this research.
